Implicit Neural Representation for Potential Field Geophysics

### 2023-10-02 authorship_declaration.tex
State percentage contribution

\smallskip{}
\noindent{}All software development was performed by L. Smith.

@@

            \textbf{Contribution}: The method was researched, developed, analysed and drafted by L. Smith, who revised the manuscript with feedback from co-authors E.J. Holden, D. Wedge, T. Horrocks, and N. Akhtar.
            As a published manuscript, further revision was undertaken prompted by peer review.
\end{itemize}

@@

            \textbf{Contribution}: Further investigation of super-resolution was initiated, developed, analysed, and prepared by L. Smith, with critical manuscript review from N. Akhtar, E.J. Holden, T. Horrocks, and D. Wedge.

@@

            \textbf{Contribution}: The concept and development of implicit neural representation for geophysics was initiated by L. Smith, who performed the subsequent research, development, analysis, and drafting. The manuscript was assisted by review from N. Akhtar, E.J. Holden, T. Horrocks, and D. Wedge.

@@

\noindent{}The contributions of the author have been truthfully stated, and permission from
each author has been sought to include the published material in this thesis.

>>>>

\smallskip{}
\noindent{}All software development for the research was performed by L. Smith.

@@

            \textbf{Contribution}: The proportion of original work by the student is \qty{80}{\percent}.
            The method was researched, developed, analysed and drafted by L. Smith, who revised the manuscript with feedback from co-authors E.J. Holden, D. Wedge, T. Horrocks, and N. Akhtar.
            As a published manuscript, further revision was undertaken prompted by peer review.
\end{itemize}

@@

            \textbf{Contribution}: The proportion of original work by the student is \qty{80}{\percent}.
            Further investigation of super-resolution was initiated, developed, analysed, and prepared by L. Smith, with critical manuscript review from N. Akhtar, E.J. Holden, T. Horrocks, and D. Wedge.

@@

            \textbf{Contribution}: The proportion of original work by the student is \qty{90}{\percent}.
            The concept and development of implicit neural representation for geophysics was initiated by L. Smith, who performed the subsequent research, development, analysis, and writing. The manuscript was assisted by review from N. Akhtar, E.J. Holden, T. Horrocks, and D. Wedge.

@@

\newpage{}
\noindent{}The contributions of the author have been truthfully stated, and permission from
each author has been sought to include the published material in this thesis.
